Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-07-29 Chapter6.tex
commiting latest

\section{pibuss, pibuss, pibuss}

@@

@@

>>>>

\section{Areas of improvement for $\pi$BUSS simulator software}

@@

% indel models
In the field of molecular biology insertion and deletion (indels) events exist on the other end of spectrum of mutations then substitution events, which we discussed in details in Subsection \ref{sub:subst_models}.
Whereas substitutions are point mutations which replace one nucleotide with another, indels proceed by either inserting or deleting nucleotides in a sequence, thus altering it's length. 
Indel mutations are well known to have a significant impact on processes of molecular evolution \citep{Fletcher2009}.
Therefore without models of insertion/deletion sequence simulation is somewhat limited.

% Without insertions/deletions, sequence simulation is very much limited. 
% This is one reason why so many sequence simulators with indels have been developed recently. 
% Since BEAGLE includes an indel model, I assume piBUSS can also include indels in its simulation. 
% If so, I highly suggest the authors to incorporate this option.
% 
% 
% We believe the reviewer is referring to the stochastic Dollo model -- this feature is indeed high on the TODO list of {\bussname} and will be implemented in a future release of the software.

@@

% rewrite, more responsive, instant color changes without re-computing

% outputting KML and web interfaces

% new analysis, spatial statistics
